---
title: "L06 Ensemble Models"
subtitle: "Data Science III (STAT 301-3)"
author: "Caleb Li"
output: 
  html_document:
    toc: true
    toc_float: true
    highlight: "tango"
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Load package(s) ----
library(tidymodels)
library(tidyverse)
library(stacks)

load("model_info/wildfires_final.rda")
load("model_info/wildfires_blend.rda")
load("data/wildfires_split.rda")
wildfires_test <- wildfires_split %>% testing()
```


## Ensemble Model
In our ensemble model, there were 41 candidate models stemming from 3 model types: the K-nearest neighbors, support vector machines using radial basis function kernel, and a linear regression. The final ensemble model retained 10 models: `svm_res_1_16` with a weight of 2.33, `lin_reg_res_1_1` with a weight of 0.838, `svm_res_1_23` with a weight of 0.494, `svm_res_1_20` with a weight of 0.111, `svm_res_1_17` with a weight of 0.0856, `knn_res_1_12` with a weight of 0.0143,`knn_res_1_13` with a weight of 0.0100,  `knn_res_1_14` with a weight of 0.00819, `knn_res_1_11` with a weight of 0.00596, `knn_res_1_10` with 0.00381

```{r}
# Load package(s) ----
wildfires_final
```

```{r}
# Show the relationship between minimizing the number of members with rmse and rsq
autoplot(wildfires_blend, type = "members") +
  theme_minimal()

# Plot the weights of the models that were included in the ensemble model
autoplot(wildfires_blend, type = "weights") +
  theme_minimal()
```

After fitting the data to the entire training set, we also obtain the predictions applied to the test set.


```{r}
# Obtain the predictions on the test set
wildfires_fit <- wildfires_test %>%
  bind_cols(predict(wildfires_final, .)) %>%
  select(burned, .pred)
wildfires_fit
```

It appears that the ensemble model obtains an RMSE of 72.9 and an R2 of 0.945.

```{r message=FALSE, warning=FALSE}
# Define a metric set
wildfires_metric <- metric_set(rmse, rsq)

# Evaluate the ensemble model
wildfires_fit %>% 
  wildfires_metric(truth = burned, estimate = .pred)

ggplot(
  data = wildfires_fit,
  mapping = aes(burned, .pred)
) +
  geom_point() +
  geom_abline(slope = 1, intercept = 0) +
  geom_smooth() +
  theme_minimal() +
  coord_obs_pred()
```

The graph above shows a that the fit is close to the linear line imposed, besides the area where it tapers off at the top right where there is an  outlier.

When comparing the ensemble model’s performance to its member models, we determine that the ensemble model obtained the lowest RMSE when compared to each of the member models individually. The model closest to achieving the RMSE of the ensemble model was the `svm_res_1_20`, which obtained an RMSE estimate of 73.4.

```{r}
# Obtain predictions for each of the individual member models
member_preds <- wildfires_test %>%
  select(burned) %>%
  bind_cols(predict(wildfires_final, wildfires_test, members = TRUE))

# Evaluate each of the individual models
map_dfr(member_preds, rmse, truth = burned, data = member_preds) %>%
  mutate(member = colnames(member_preds))
```


## Github Repo Link

[https://github.com/STAT301III/L06-ensemble-models-calebthedoge](https://github.com/STAT301III/L06-ensemble-models-calebthedoge){target="_blank"}

